Democracy, Public Support, and Measurement Uncertainty

### 2021-06-24 paper/dcpo_demsupport.Rmd
downloading data from the osf

# load all the packages you will use below 
p_load(
  # data scrapping
  dataverse, 
  DCPOtools, mitools,
  boot, 
  here,
  # analysis
  plm, 
  rstan, 
  # presentation
  flextable, 
  broomExtra, 
  kableExtra, 
  modelsummary, 
  gridExtra,
  latex2exp,
  drhutools,
  dotwhisker, 
  # data wrangling
  tidyverse, 
  janitor, 
  glue, 
  qs
)

@@

# produced by cls_ajps_apsr_uncertain.R and dcpo_ajps_apsr_uncertain.R
load(here("data", "cls_ajps.rda")) 
load(here("data", "dcpo_ajps.rda")) 
load(here("data", "cls_apsr.rda"))
load(here("data", "dcpo_apsr.rda"))

claassen_replication <- readRDS(here("data", "claassen_replication.rds")) %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)
load(here("data", "claassen_m5_theta.rda"))
load(here("data", "dem_mood_apsr.RData"))
load(here("data", "dcpo_input.rda"))
load(here("data", "dcpo_theta.rda"))
load(here("data", "dcpo_sigma.rda"))
#load(here("data", "dcpo_ajps_rubin.rda"))
# df_controls <- readRDS(here("data", "control_variables_ajps.rds"))   #use control file for merging with 
df_dcpoUncertainAPSR <- readRDS(here("data", "df_dcpoUncertainAPSR.rds"))

>>>>

# load all the packages you will use below 
p_load(
  # data scrapping
  dataverse, 
  osfr,
  # DCPOtools, 
  mitools,
  boot, 
  here,
  # analysis
  plm, 
  rstan, 
  # presentation
  flextable, 
  broomExtra, 
  kableExtra, 
  modelsummary, 
  gridExtra,
  latex2exp,
  drhutools,
  dotwhisker, 
  # data wrangling
  tidyverse, 
  janitor, 
  glue, 
  qs
)

@@

# Removed the comments for the final replication file
## Claasseen and extend data

# osf_retrieve_file("hczmf") %>% 
#     osf_download(path = "../data")
# 
# osf_retrieve_file("wbu6m") %>% 
#     osf_download(path = "../data")
# 
# osf_retrieve_file("2jhbc") %>% 
#     osf_download(path = "../data")
# 
# osf_retrieve_file("u96m8") %>% 
#     osf_download(path = "../data")

load(here("data", "pure_cls_ajps.rda")) 
load(here("data", "pure_cls_apsr.rda")) 
load(here("data", "exp_cls_ajps.rda"))
load(here("data", "exp_cls_apsr.rda"))
